---
title: "Comparing Motor Vehicles"
author: "Brandon Hansen"
date: "8/7/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Application Pitch

This application allows the user to easily compare between different motor vehicles and allows them too

- Gain insights into different motor vehicle correlations
- Do exploratory data analysis on motor vehicles
- Plan out future classification and regression tasks for motor vehicles

## Functionality Part One

The application displays a plot with motor vehicles being compared by weight and MPG.

```{r echo=FALSE}
plot(mtcars$wt, mtcars$mpg, xlab="Weight", ylab="MPG")
```


## Functionality Part Two

The application analyses can be divided between automatic and manual transmission vehicles through parameter selection.

```{r echo=FALSE}
auto <- subset(mtcars, am == 0)
manl <- subset(mtcars, am == 1)
plot(auto$wt, auto$mpg, col="red", xlab="Weight", ylab="MPG")
points(manl$wt, manl$mpg, col="blue")
```

## Functionality Part Three

Analysis can be further divided between individual cylinders to compare performance versus weight in automatic and manual vehicles.

```{r}
auto4 <- subset(mtcars, am == 0 & cyl == 4)
manl4 <- subset(mtcars, am == 1 & cyl == 4)
auto6 <- subset(mtcars, am == 0 & cyl == 6)
manl6 <- subset(mtcars, am == 1 & cyl == 6)
auto8 <- subset(mtcars, am == 0 & cyl == 8)
manl8 <- subset(mtcars, am == 1 & cyl == 8)
par(mfrow=c(2,2))
plot(auto4$wt, auto4$mpg, col="red", xlab="Weight", ylab="MPG")
points(manl4$wt, manl4$mpg, col="blue", xlab="Weight", ylab="MPG")
plot(auto6$wt, auto6$mpg, col="red", xlab="Weight", ylab="MPG")
points(manl6$wt, manl6$mpg, col="blue", xlab="Weight", ylab="MPG")
plot(auto8$wt, auto8$mpg, col="red", xlab="Weight", ylab="MPG")
points(manl8$wt, manl8$mpg, col="blue", xlab="Weight", ylab="MPG")
```

